### 2018-05-02 paper/evaluation.tex
new figure
minor

\commentDaniel{%
  Some data for Adrien.%
}
\Textcite{ANOBE} proposed using a modified version of \ac{KD-HES}.

@@

\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
\caption{ \label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.}
\end{figure}

HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM, while figure~\ref{fig:sample_usage} shows an observation sequence $O$ that was generated from the displayed model.

Each round lasts $T=10s$ \commentAL{yes, the user switches places fast} and users start at different times. 
This way, even though the round period is fixed, devices enter and leave the system at different points in the continuous time.

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}

\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
}
\end{figure}

@@

In the following, we perform two types of experiments: figures~\ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} illustrate the establishment of PORs, while the next ones measure file transfer.

Figures \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
$\theta$ is the threshold of the probability that all nodes fail at once: we keep adding nodes to a layer until the layer's probability is below $\theta$. 
It takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step.
It is measured in time periods $T$, the interval at which users change the connection state of their devices.
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.

@@

We first measure the influence of the parameter $\theta$ on the number of nodes per layer in figure~\ref{fig:nodes_per_layer_vs_theta}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
The mean required number of devices per layer is reasonable: between 2 and 6.
Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.

@@

We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
We consider a route available if at least one node per layer is online at this time.
The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
First of all, we observe that time has a negligible impact on the availability of routes. 
This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
We also see that $\theta$ has a big impact on the availability average, and variability.
Still, $\theta\in[10^-4, 10^-3]$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
Combined with the results from figure~\ref{fig:nodes_per_layer_vs_theta}, it means that routes will need an average of 5-6 devices per layer to be highly available.
Finally, increasing $L$ logically hinders the results when using low-availability layers.

We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
The counterpart is that messages header size grows \commentAL{How does it grow? Quadratically, exponentially?} with the number of layers and the number of devices per layer.
Considering that most onion routing solutions use a statically defined message size to avoid information leakage, this means that a more reliable onion route comes at the cost of an increased network traffic.

\subsection{File transfer} % (fold)
\label{sub:file_transfer}

>>>>

In the following, we present the evaluation results of \name. 
We first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the PORs creation  in section~\ref{sub:predictive_onion_routes_creation}, to conclude with an overall evaluation of the file transfer performance in section~\ref{sub:file_transfer}.

@@

\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
\vspace{2ex}
\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}

\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior: on top are the HMM parameters, on the middle is a visual representation of the model, and on the bottom is a sample output from the model.}
\end{figure}

HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM $\lambda_N$, its graphical representation, along with a sample observation sequence $O$ output from the model $\lambda_N$.

Each round lasts $T=10s$ and users start at different times. 
This way, even though the round period is fixed, devices enter and leave the system at different points in the continuous time.

@@

In the following, we perform two types of experiments: 
section~\ref{sub:predictive_onion_routes_creation} evaluates the establishment of PORs, while section~\ref{sub:file_transfer} handles file transfer.
For that reason, they used different parameter sets.

\paragraph*{PORs creation}
Figures \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
$\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step.
It is measured in time periods $T$, the interval at which users change the connection state of their devices.
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.

@@

We first measure the influence of the parameter $\theta$ on the number of nodes per layer in figure~\ref{fig:nodes_per_layer_vs_theta}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
The mean number of devices per layer lies between 2 and 6.
Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.

@@

We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
We consider a route available if at least one node per layer is online at this time.
The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
First of all, we observe that time has a negligible impact on the availability of routes. 
This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
We also see that $\theta$ has a big impact on the mean availability and its variability.
Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
Combined with the results from figure~\ref{fig:nodes_per_layer_vs_theta}, it means that routes will need an average of 5-6 devices per layer to be highly available.
Finally, increasing $L$ logically hinders the results when using low-availability layers.

\\
We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
The counterpart is that messages header size grows with the number of layers and the number of devices per layer.

Considering that most onion routing solutions use a statically defined message size to avoid information leakage, a bigger header means less space for the payload in each message. The more reliable the route, the bigger the number of messages per file. There is a trade-off between route reliability and network traffic.

\subsection{File transfer time} % (fold)
\label{sub:file_transfer}
